Self Regulation Ontology Retest Analyses

### 2018-06-07 code/SRO_Retest_Analyses.Rmd
cleanup

```{r warning=FALSE, message=FALSE}
tmp = measure_labels %>%
  mutate(dv = as.character(dv),
         contrast = ifelse(overall_difference == "difference", "contrast", "non-contrast")) %>%
  filter(ddm_task == 1, 
         #overall_difference != "condition",
         rt_acc != 'other') %>%
  drop_na() %>%
  left_join(boot_df[,c("dv", "icc")], by = 'dv')

tmp = tmp %>%
  drop_na() %>% #try removing this in final release
  group_by(contrast, raw_fit, rt_acc) %>%
  summarise(icc_median = quantile(icc, probs = 0.5),
            icc_2.5 = quantile(icc, probs = 0.025),
            icc_97.5 = quantile(icc, probs = 0.975),
            num_vars = n()/1000)

tmp %>% 
  datatable() %>%
  formatRound(columns=c('icc_median', 'icc_2.5', 'icc_97.5'), digits=3)
```

```{r}
tmp_save = tmp %>%
  ungroup() %>%
  mutate(contrast = as.character(contrast),
         raw_fit = as.character(raw_fit),
         rt_acc = as.character(rt_acc)) %>%
  arrange(-icc_median)

@@

Comparing overall vs difference: overall has higher reliability than difference.

```{r}
summary(lmerTest::lmer(icc ~ overall_difference + (1|dv) ,tmp))
```

"consistent with the summing of variance in the difference score"

```{r}
tmp = measure_labels %>%
  mutate(dv = as.character(dv)) %>%
  filter(ddm_task == 1, 
         overall_difference != "condition",
         rt_acc != 'other') %>%
  drop_na() %>%
  left_join(boot_df[,c("dv", "icc", "var_subs","var_ind", "var_resid")], by = 'dv') %>%
  mutate(var_subs_pct = var_subs/(var_subs+var_ind+var_resid),
         var_ind_pct = var_ind/(var_subs+var_ind+var_resid), 
         var_resid_pct = var_resid/(var_subs+var_ind+var_resid)) %>%
  select(-task, -ddm_task, -num_all_trials, -var_resid, -var_subs, -var_ind) %>%
  gather(key, value, -dv, -overall_difference, -raw_fit, -rt_acc, -icc)

tmp %>%
  filter(key == "var_resid_pct") %>%
  ggplot(aes(raw_fit, value, fill=overall_difference))+
  geom_boxplot()

summary(lmer(value  ~ overall_difference*raw_fit + (1|dv), data=tmp %>% filter(key=="var_resid_pct")))

#Simple effects
summary(lmer(value  ~ overall_difference + (1|dv), data=tmp %>% filter(key=="var_resid_pct", raw_fit== "EZ")))

summary(lmer(value  ~ overall_difference + (1|dv), data=tmp %>% filter(key=="var_resid_pct", raw_fit== "raw")))

summary(lmer(value  ~ overall_difference + (1|dv), data=tmp %>% filter(key=="var_resid_pct", raw_fit== "hddm")))
```

Checking Rogosa's claim that ‘Difference scores are reliable when individual differences in true change exist.’
How do we measure ‘individual difference in true change’ 
1.between subject variability in difference score distributions
2.within subject variance in icc
Using 2 (because comparable between subject variance across different measures would be hard)
Expecting to see: positive correlation between mean icc and mean var_ind_pct
Result: The correlation between mean icc and mean var ind pct is NOT significant BUT looking at the distribution of mean var ind pct there is not a lot of variability t

```{r}
tmp = tmp %>%
  spread(key, value) %>%
  group_by(dv) %>%
  summarise(mean_var_ind_pct = mean(var_ind_pct),
            mean_var_subs_pct = mean(var_subs_pct),
            mean_icc = mean(icc)) %>%
  left_join(measure_labels, by='dv')

tmp %>%
  filter(overall_difference == 'difference') %>%
  ggplot(aes(mean_var_ind_pct, mean_icc))+
  geom_point()+
  geom_abline(slope=1, intercept=0)+
  geom_smooth(method = "lm")

summary(lm(mean_icc ~ mean_var_ind_pct,data=tmp %>%
  filter(overall_difference == 'difference')))

tmp %>%
  filter(overall_difference == 'difference') %>%
  ggplot(aes(mean_var_ind_pct))+
  geom_density()

summary(tmp$mean_var_ind_pct[tmp$overall_difference == "difference"])
summary(tmp$mean_var_subs_pct[tmp$overall_difference == "difference"])

tmp = tmp %>% filter(overall_difference == 'difference')
t.test(tmp$mean_var_ind_pct, tmp$mean_var_subs_pct, paired=T)
```

```{r}
tmp = measure_labels %>%
  mutate(dv = as.character(dv)) %>%
  filter(ddm_task == 1, 
         overall_difference != "condition",
         rt_acc != 'other') %>%
  drop_na() %>%
  left_join(boot_df[,c("dv", "icc", "spearman")], by = 'dv')
```

@@

```{r}
summary(lmerTest::lmer(icc ~ raw_fit + (1|dv) ,tmp %>% filter(overall_difference == "overall")))
```

@@

```{r}
summary(lmerTest::lmer(icc ~ raw_fit + (1|dv) ,tmp %>% filter(overall_difference == "difference")))
```

```{r}
tmp %>%
  ggplot(aes(factor(raw_fit, levels = c("raw", "EZ", "hddm"), labels=c("Raw", "EZ-diffusion", "Hierarchical diffusion")), icc, fill=factor(rt_acc, levels = c("rt","accuracy", "drift rate", "threshold", "non-decision"), labels=c("Response Time", "Accuracy","Drift Rate", "Threshold", "Non-decision"))))+
  geom_boxplot()+
  facet_wrap(~factor(overall_difference, levels=c("overall", "difference"), labels=c("Overall", "Difference")))+
  theme_bw()+
  ylab("ICC")+
  xlab("")+
  theme(legend.title = element_blank(),
        legend.position = 'bottom',
        legend.text = element_text(size=16),
        strip.text = element_text(size=16),
        axis.text = element_text(size = 16),
        text = element_text(size=16))+
  guides(fill = guide_legend(ncol = 2))+
  scale_fill_discrete(breaks=c("Drift Rate", "Threshold", "Non-decision", "Response Time", "Accuracy"))

@@

```{r}
tmp2 = measure_labels %>%
  mutate(dv = as.character(dv)) %>%
  filter(ddm_task == 1, 
         overall_difference != "condition",
         rt_acc != "other",
         raw_fit != "hddm") %>%
  drop_na() %>%
  left_join(rel_df[,c("dv", "icc", "spearman")], by = 'dv')

tmp2 %>%
  # filter(overall_difference == "overall") %>%
  ggplot(aes(factor(raw_fit, levels = c("raw", "EZ", "hddm"), labels=c("Raw", "EZ-diffusion", "Hierarchical diffusion")), icc, fill=factor(rt_acc, levels = c("rt","accuracy", "drift rate", "threshold", "non-decision"), labels=c("Response Time", "Accuracy","Drift Rate", "Threshold", "Non-decision"))))+
  geom_boxplot()+
  facet_wrap(~factor(overall_difference, levels=c("overall", "difference"), labels=c("Overall (all trials)", "Difference (contrasting conditions)")))+
  theme_bw()+
  ylab("ICC")+
  xlab("")+
  theme(legend.title = element_blank(),
        legend.position = 'bottom',
        legend.text = element_text(size=16),
        strip.text = element_text(size=16),
        axis.text = element_text(size = 16),
        text = element_text(size=16))+
  guides(fill = guide_legend(ncol = 2))+
  scale_fill_discrete(breaks=c("Drift Rate", "Threshold", "Non-decision", "Response Time", "Accuracy"))+
  ylim(-0.4, 1)

@@

```{r warning=FALSE, message=FALSE}
tmp = measure_labels %>%
  mutate(dv = as.character(dv)) %>%
  filter(task == 'survey') %>%
  left_join(boot_df[,c("dv", "icc", "spearman")], by = 'dv') %>%
  filter(overall_difference != 'difference' & raw_fit %in% c('EZ', 'hddm') == FALSE)%>%
  separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.',remove=FALSE) %>%
  select(-extra_1, -extra_2) %>%
  group_by(task_name) %>%
  summarise(median_icc = median(icc),
            median_spearman = median(spearman),
            icc_2.5 = quantile(icc, probs = 0.025),
            icc_97.5 = quantile(icc, probs = 0.975),
            min_spearman = min(spearman),
            max_spearman = max(spearman),
            num_measures = n()/1000,
            mean_num_trials = round(mean(num_all_trials)))%>%
  arrange(-median_icc, -median_spearman)

tmp %>%
  datatable() %>%
  formatRound(columns=c('median_spearman', 'median_icc',
                        'min_spearman', 'icc_2.5',
                        'max_spearman', 'icc_97.5'), digits=3)
```

```{r}
tmp = tmp%>%
  select(-min_spearman, -max_spearman,-median_spearman) %>%
  mutate(task_name = gsub("_", " ", task_name),
         task_name = gsub("(^|[[:space:]])([[:alpha:]])", "\\1\\U\\2", task_name, perl=TRUE),
         task_name = gsub("Survey", "", task_name))

sjt.df(tmp %>% mutate_if(is.numeric, funs(round(., 3))), describe=F, hide.progress = TRUE, show.rownames = FALSE, file = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/tables/survey_rel_table.doc")
```

@@

```{r warning=FALSE, message=FALSE}
tmp = measure_labels %>%
  mutate(dv = as.character(dv)) %>%
  filter(task == 'survey') %>%
  # left_join(rel_df[,c("dv", "spearman","icc")], by='dv') %>%
  left_join(boot_df[,c("dv", "spearman","icc")], by='dv') %>%
  filter(overall_difference != 'difference' & raw_fit %in% c('EZ', 'hddm') == FALSE)%>%
  separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.',remove=FALSE) %>%
  select(-extra_1, -extra_2)

```{r warning=FALSE, message=FALSE}
measure_labels %>%
  mutate(dv = as.character(dv)) %>%
  filter(task == 'task') %>%
  # left_join(rel_df[,c("dv", "spearman","icc")], by='dv') %>%
  left_join(boot_df[,c("dv", "spearman","icc")], by='dv') %>%
  filter(overall_difference != 'difference' & raw_fit %in% c('EZ', 'hddm') == FALSE)%>%
  separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.',remove=FALSE) %>%
  select(-extra_1, -extra_2) %>%
  ggplot(aes(num_all_trials, icc))+
  geom_point()+
  geom_smooth(method="lm")+
  theme_bw()+
  xlab("Number of trials")+
  ylab("ICC")
```

>>>>

```{r warning=FALSE, message=FALSE}
tmp = measure_labels %>%
  mutate(dv = as.character(dv),
         contrast = ifelse(overall_difference == "difference", "contrast", "non-contrast")) %>%
  filter(ddm_task == 1, 
         rt_acc != 'other') %>%
  drop_na() %>%
  left_join(boot_df[,c("dv", "icc")], by = 'dv')

tmp_save = tmp %>%
  drop_na() %>% #try removing this in final release
  group_by(contrast, raw_fit, rt_acc) %>%
  summarise(icc_median = quantile(icc, probs = 0.5),
            icc_2.5 = quantile(icc, probs = 0.025),
            icc_97.5 = quantile(icc, probs = 0.975),
            num_vars = n()/1000)

tmp_save %>% 
  datatable() %>%
  formatRound(columns=c('icc_median', 'icc_2.5', 'icc_97.5'), digits=3)
```

```{r}
tmp_save = tmp_save %>%
  ungroup() %>%
  mutate(contrast = as.character(contrast),
         raw_fit = as.character(raw_fit),
         rt_acc = as.character(rt_acc)) %>%
  arrange(-icc_median)

@@

Comparing contrast vs non-contrast: overall has higher reliability than difference.

```{r}
summary(lmerTest::lmer(icc ~ contrast + (1|dv) ,tmp))
```

@@

```{r}
summary(lmerTest::lmer(icc ~ raw_fit + (1|dv) ,tmp %>% filter(contrast == "non-contrast")))
```

@@

```{r}
summary(lmerTest::lmer(icc ~ raw_fit + (1|dv) ,tmp %>% filter(contrast == "contrast")))
```

```{r}
tmp %>%
  ggplot(aes(factor(raw_fit, levels = c("raw", "EZ", "hddm"), labels=c("Raw", "EZ-diffusion", "Hierarchical diffusion")), icc, fill=factor(rt_acc, levels = c("rt","accuracy", "drift rate", "threshold", "non-decision"), labels=c("Response Time", "Accuracy","Drift Rate", "Threshold", "Non-decision"))))+
  geom_boxplot()+
  facet_wrap(~factor(contrast, levels=c("non-contrast", "contrast"), labels=c("Non-contrast", "Contrast")))+
  theme_bw()+
  ylab("ICC")+
  xlab("")+
  theme(legend.title = element_blank(),
        legend.position = 'bottom',
        legend.text = element_text(size=16),
        strip.text = element_text(size=16),
        axis.text = element_text(size = 16),
        text = element_text(size=16))+
  guides(fill = guide_legend(ncol = 2))+
  scale_fill_discrete(breaks=c("Drift Rate", "Threshold", "Non-decision", "Response Time", "Accuracy"))

@@

```{r}
tmp2 = measure_labels %>%
  mutate(dv = as.character(dv),
         contrast = ifelse(overall_difference == "difference", "contrast", "non-contrast")) %>%
  filter(ddm_task == 1, 
         rt_acc != 'other') %>%
  drop_na() %>%
  left_join(rel_df[,c("dv", "icc")], by = 'dv')

tmp2 %>%
  ggplot(aes(factor(raw_fit, levels = c("raw", "EZ", "hddm"), labels=c("Raw", "EZ-diffusion", "Hierarchical diffusion")), icc, fill=factor(rt_acc, levels = c("rt","accuracy", "drift rate", "threshold", "non-decision"), labels=c("Response Time", "Accuracy","Drift Rate", "Threshold", "Non-decision"))))+
  geom_boxplot()+
  facet_wrap(~factor(contrast, levels=c("non-contrast", "contrast"), labels=c("Non-contrast", "Contrast")))+
  theme_bw()+
  ylab("ICC")+
  xlab("")+
  theme(legend.title = element_blank(),
        legend.position = 'bottom',
        legend.text = element_text(size=16),
        strip.text = element_text(size=16),
        axis.text = element_text(size = 16),
        text = element_text(size=16))+
  guides(fill = guide_legend(ncol = 2))+
  scale_fill_discrete(breaks=c("Drift Rate", "Threshold", "Non-decision", "Response Time", "Accuracy"))+
  ylim(-0.4, 1)

@@

```{r warning=FALSE, message=FALSE}
tmp = measure_labels %>%
  mutate(dv = as.character(dv)) %>%
  filter(task == 'survey') %>%
  left_join(boot_df[,c("dv", "icc")], by = 'dv') %>%
  separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.',remove=FALSE) %>%
  select(-extra_1, -extra_2)

tmp_save = tmp %>%
  group_by(task_name) %>%
  summarise(median_icc = median(icc),
            icc_2.5 = quantile(icc, probs = 0.025),
            icc_97.5 = quantile(icc, probs = 0.975),
            num_measures = n()/1000,
            mean_num_trials = round(mean(num_all_trials)))%>%
  arrange(-median_icc)

tmp_save %>%
  datatable() %>%
  formatRound(columns=c('median_icc', 'icc_2.5','icc_97.5'), digits=3)
```

```{r}
tmp_save = tmp_save%>%
  mutate(task_name = gsub("_", " ", task_name),
         task_name = gsub("(^|[[:space:]])([[:alpha:]])", "\\1\\U\\2", task_name, perl=TRUE),
         task_name = gsub("Survey", "", task_name))

names(tmp_save) = gsub("_", " ", names(tmp_save))
names(tmp_save) = gsub("(^|[[:space:]])([[:alpha:]])", "\\1\\U\\2", names(tmp_save), perl=TRUE)

sjt.df(tmp_save %>% mutate_if(is.numeric, funs(round(., 3))), describe=F, hide.progress = TRUE, show.rownames = FALSE, file = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/tables/survey_rel_table.doc")
```

@@

```{r warning=FALSE, message=FALSE}
summary(lmerTest::lmer(icc ~ num_all_trials + (1|dv), data = tmp))
```
